---
title: "fb_babi_data"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
```

Download here:
https://venturebeat.com/2016/02/18/facebook-releases-1-6gb-data-set-of-childrens-stories-for-training-its-ai/

Preposition data
Look at read me and file sizes
"Data is in the included "data" folder. Questions are separated according to whether the missing word is a named entity (NE), common noun (CN), verb (V) or preposition (P). The POS/NER was done by Stanford CoreNLP and nothing else. Thus the dataset consists of the following files:"


"Data is in the included "data" folder. Questions are separated according to whether the missing word is a named entity (NE), common noun (CN), verb (V) or preposition (P). The POS/NER was done by Stanford CoreNLP and nothing else. Thus the dataset consists of the following files:


cbtest_NE_train.txt : 67128 questions
cbtest_NE_valid_2000ex.txt : 2000
cbtest_NE_test_2500ex.txt : 2500

cbtest_CN_train.txt : 121176 questions
cbtest_CN_valid_2000ex.txt : 2000
cbtest_CN_test_2500ex.txt : 2500

cbtest_V_train.txt : 109111 questions
cbtest_V_valid_2000ex.txt : 2000
cbtest_V_test_2500ex.txt : 2500

cbtest_P_train.txt : 67128 questions
cbtest_P_valid_2000ex.txt : 2000
cbtest_P_test_2500ex.txt : 2500

These files, the text is in the format of CBT questions (see below). We also release the raw text from test / valid / train sets, again tokenised by Stanford Core NLP. These files have the form cbt_{train, valid, test}.txt

Detailed stats of all question types are given in the "stats" folder."

```{r}
cb_data_test <- "~/Downloads/CBTest/data/cbtest_P_train.txt"
prep_data <- read_tsv(cb_data_test, col_names = F)
```


```{r}
prep_data
```

Load the wordbank words

```{r}
base::load("~/GitHub_C/wordbank-book/data/psychometrics/eng_ws_mods_4pl.Rds")

wordbank_words <- coefs_4pl %>% pull(definition)
```


Filter for rows containing wordbank words

```{r}
prep_data %>% 
  filter(
    str_detect(X1, wordbank_words)
  ) 
```


