---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

This notebook is for recreating the relevant plots from wordbank:
Source: https://wordbank-book.stanford.edu/psychometrics.html
Code adapted from: https://github.com/langcog/wordbank-book

```{r}
library(tidyverse)
#install.packages("wordbankr")
library(wordbankr)
library(ggstance)
```

Load items from wordbank

```{r}
items <- get_item_data(language = "English (American)", form = "WS")
```

Load data from psychometrics

```{r}
base::load("~/GitHub_C/wordbank-book/data/psychometrics/eng_ws_raw_data.Rds")

d_ws <- eng_ws %>%
  mutate(produces = value == "produces") %>%
  filter(!is.na(category)) %>%
  select(data_id, produces, age, production, sex, definition) 

base::load("~/GitHub_C/wordbank-book/data/psychometrics/eng_ws_mods_2pl.Rds")

d_ws_summary <- d_ws %>%
  group_by(data_id, sex, age) %>%
  summarise(production = production[1]) %>%
  right_join(fscores_2pl %>%
               mutate(data_id = as.numeric(data_id))) %>%
  filter(!is.na(sex))
```


Figure 4.5: Item characteristic curves for a set of individual items from the English WS sample.

```{r}
thetas <- seq(-6,6,.1)
irt4pl <- function(a, d, g, u, theta = seq(-6,6,.1)) {
  p = g + (u - g) * boot::inv.logit(a * (theta + d))
  return(p)
}
irt2pl <- function(a, d, theta = seq(-6,6,.1)) {
  p = boot::inv.logit(a * (theta + d))
  return(p)
}

examples <- c("table","mommy*","trash","yesterday")
iccs <- coefs_2pl %>%
  filter(definition %in% examples) %>%
  split(.$definition) %>%
  map_df(function(d) {
    return(data_frame(definition = d$definition,
                      theta = thetas, 
                      p = irt2pl(d$a1, d$d, thetas)))
  })

ggplot(iccs,  
       aes(x = theta, y = p)) + 
  geom_line() + 
  facet_wrap(~definition) + 
  xlab("Ability") + 
  ylab("Probability of production")
```

Figure 4.6: Words (points), plotted by their difficulty and discrimination parameters, as recovered by the 2-parameter IRT model (see text). Outliers are labeled.

```{r, message = FALSE, warning = FALSE}
ggplot(coefs_2pl,  
       aes(x = a1, y = -d)) + 
  geom_point(alpha = .3) + 
  ggrepel::geom_text_repel(data = filter(coefs_2pl, 
                                -d < -3.8 | -d > 5.3 | a1 > 4 | a1 < 1), 
                  aes(label = definition), size = 3) + 
  xlab("Discrimination") + 
  ylab("Difficulty")
```

Figure 4.7: Words (points), plotted now by their lower and upper bound parameters from the 4-parameter IRT model.


```{r, message = FALSE, warning = FALSE}
base::load("~/GitHub_C/wordbank-book/data/psychometrics/eng_ws_mods_4pl.Rds")

ggplot(coefs_4pl, aes(x = g, y = u)) + 
  geom_point(alpha = .3) + 
  ggrepel::geom_text_repel(data = filter(coefs_4pl, 
                                abs(g) > .4 | u < .75), 
                  aes(label = definition), size = 3) + 
  xlab("Lower bound (high base rate)") + 
  ylab("Upper bound (not known by many)")
```

Figure 4.8: Histograms of words’ difficulty and discrimination parameters, for comprehension and production.

```{r, message = FALSE, warning = FALSE}
library(cowplot)
base::load("~/GitHub_C/wordbank-book/data/psychometrics/eng_wg_mods_2pl.Rds")

coefs_2pl_wg <- bind_rows(coefs_2pl_wg_produces %>%
                            mutate(measure = "Produces"),
                          coefs_2pl_wg_understands %>%
                            mutate(measure = "Understands"))

wg_comp_prod <- 
  coefs_2pl_wg %>%
  select(a1, d, measure) %>%
  gather(parameter, value, a1, d) %>%
  mutate(parameter = fct_recode(parameter, 
                                Discrimination = "a1", 
                                Difficulty = "d") %>%
           relevel("Difficulty"),
         measure = fct_relevel(measure, "Understands"))

ggplot(wg_comp_prod, 
       aes(x = value)) +
  geom_histogram(binwidth = .5) + 
  facet_grid(measure ~ parameter) + 
  # xlim(-5,5) + 
  xlab("Parameter value") + 
  ylab("Number of words") 


wg_comp_prod_summary <- wg_comp_prod %>%
  group_by(measure, parameter) %>%
  summarise(value = mean(value))
```

4.3.3 Lexical category effects on item performance

```{r, message = FALSE, warning = FALSE}
coefs_2pl <- 
  coefs_2pl %>%
  left_join(
    items %>% 
    filter(language == "English (American)", form == "WS")
  ) %>%
  mutate(
    lexical_class_label = 
      lexical_class %>% factor() %>% fct_relabel(~.x %>% as.character())
  )

class_summary <- coefs_2pl %>%
  group_by(lexical_class, lexical_class_label) %>%
  summarise(sd_a1 = sd(a1, na.rm=TRUE), 
            a1 = mean(a1))

a <- ggplot(coefs_2pl, 
       aes(x = a1, y = -d, col = lexical_class_label)) + 
  geom_point(alpha = .3) + 
  ggrepel::geom_text_repel(data = filter(coefs_2pl, 
                                a1 < 1 | a1 > 3.8 | -d > 5 | -d < -2.5), 
                  aes(label = definition), size = 2,
                  show.legend = FALSE) + 
  scale_colour_discrete(name = "Lexical class") + 
  xlab("Discrimination") + 
  ylab("Difficulty")

b <- ggplot(coefs_2pl, 
       aes(x = a1, fill = lexical_class_label)) + 
  geom_histogram() + 
  scale_fill_discrete(name = "Lexical class") + 
  xlab("Discrimination") +
  ylab("Number of words") +
  xlim(0,4)

gridExtra::grid.arrange(a, b)
```


```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  write_csv("~/wordbank_words.csv")
```


Sort by category

```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  count(category, sort = T)
```

#locations

```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  filter(category == "locations")
```
#helping_verbs

```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  filter(category == "helping_verbs")
```

#quantifiers

```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  filter(category == "quantifiers")
```
#connecting_words

```{r}
coefs_2pl %>% 
  select(definition, category) %>% 
  filter(category == "connecting_words")
```


```{r}
coefs_2pl %>% 
  select(value = definition, category) %>% 
  mutate(
    value = if_else(value == "buttocks/bottom*", "buttocks", value),
    value = if_else(value == "call (on phone)", "call", value),
    value = if_else(value == "church*", "church", value),
    value = if_else(value == "daddy*", "daddy", value),
    value = if_else(value == "did/did ya", "did", value),
    value = if_else(value == "dress (object)", "dress", value),
    value = if_else(value == "gonna/going to", "going to", value),
    value = if_else(value == "gotta/got to", "got to", value),
    value = if_else(value == "grandma*", "grandma", value),
    value = if_else(value == "grandpa*", "grandpa", value),
    value = if_else(value == "hafta/have to", "have to", value),
    value = if_else(value == "inside/in", "inside", value),
    value = if_else(value == "lemme/let me", "let me", value),
    value = if_else(value == "little (description)", "little", value),
    value = if_else(value == "mommy*", "mommy", value),
    value = if_else(value == "need/need to", "need to", value),
    value = if_else(value == "owie/boo boo", "boo boo", value),
    value = if_else(value == "penis*", "penis", value),
    value = if_else(value == "shh/shush/hush", "shush", value),
    value = if_else(value == "soda/pop", "soda", value),
    value = if_else(value == "tissue/kleenex", "tissue", value),
    value = if_else(value == "toy (object)", "toy", value),
    value = if_else(value == "vagina*", "vagina", value),
    value = if_else(value == "wanna/want to", "want to", value)
  ) %>% 
  #polysemy
  filter(
    !value %in% 
      c(
        "can (auxiliary)", "can (object)", 
        "chicken (food)", "chicken (animal)", 
        "clean (description)", "clean (action)",
        "drink (beverage)", "drink (action)",
        "dry (description)", "dry (action)",
        "fish (food)", "fish (animal)",
        "orange (food)", "orange (description)",
        "slide (object)", "slide (action)",
        "swing (object)", "swing (action)",
        "watch (object)", "watch (action)",
        "water (not beverage)", "water (beverage)",
        "work (place)", "work (action)"
        )
  ) %>% 
  #some quantifiers
  filter(
    !value %in% 
      c("a", "am", "an", "the")
  ) %>% 
  #connecting words
  filter(
    !value %in%
      c("and", "because", "but", "if", "so", "then")
  ) %>% 
  #helping verbs
  filter(
    !value %in% 
      c("am", "are", "be", "can (auxiliary)", "could", "did/did ya", "do", "does", 
        "don't", "gonna/going to", "gotta/got to", "hafta/have to", "is", "lemme/let me", 
        "need/need to", "try/try to", "wanna/want to", "was", "were", "will", "would")
  ) %>% 
  write_tsv("~/worbank_with_category.tsv")
```



IRT comparison begins here

Load in IRT parameters from all of the generative models

```{r}
irt_model_files <- 
  c("RUN_29_GPU_14_models_Childes_all_words_item_parameters.txt",
    "RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt",
    "RUN_30_GPU_14_models_babi_all_words_item_parameters.txt"
    )

irt_read_fun <- function(model_path){
  
  full_path <- str_c("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/", model_path)
  
  read_tsv(full_path, col_names = F, skip = 1) %>% 
    select(definition = X2, discrim_ml = X3, diff_ml = X4) %>% 
    mutate(path = model_path)
  
}

all_irt_item_outputs_gen <- 
  irt_model_files %>% 
  map_df(irt_read_fun) %>% 
  mutate(task = "generation")
```


Load in IRT parameters from the discriminative models

```{r}
irt_model_discrim <- 
  c("both_datasets_40_20_irt_models_item_parameters.txt",
    "childes_20_20_item_parameters.txt",
    "babi_20_20_item_parameters.txt"
    )

irt_read_fun_discrim <- function(model_path){
  
  full_path <- str_c("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/discriminative/", model_path)
  
  read_tsv(full_path, col_names = F, skip = 1) %>% 
    select(definition = X2, discrim_ml = X3, diff_ml = X4) %>% 
    mutate(path = model_path)
  
}

all_irt_item_outputs_discrim <- 
  irt_model_discrim %>% 
  map_df(irt_read_fun_discrim) %>% 
  mutate(task = "discrimination")
```


Combine the data

```{r}
all_irt_item_outputs <- 
  all_irt_item_outputs_gen %>% 
  rbind(all_irt_item_outputs_discrim)
```


Join irt parameters from models with wordbank

```{r}
irt_params_joined <- 
  all_irt_item_outputs %>% 
  filter(task == "generation") %>% 
  left_join(
    coefs_2pl_wg %>% 
    select(definition, discrim_word = a1, diff_wrd = d, measure) %>% 
    filter(measure == "Produces") %>% 
    left_join(
      coefs_2pl %>% 
      select(definition, category, lexical_class),
      by = "definition"
    ),
    by = "definition"
  ) %>% 
  rbind(
    all_irt_item_outputs %>% 
    filter(task == "discrimination") %>% 
    left_join(
      coefs_2pl_wg %>% 
      select(definition, discrim_word = a1, diff_wrd = d, measure) %>% 
      filter(measure == "Understands") %>% 
      left_join(
        coefs_2pl %>% 
        select(definition, category, lexical_class),
        by = "definition"
      ),
      by = "definition"
    )
  ) %>% 
  drop_na(lexical_class) %>% 
  mutate(
    lexical_class_label = 
      lexical_class %>% factor() %>% fct_relabel(~.x %>% as.character())
  )
```

Correlations

For each model
```{r}
irt_params_joined %>% 
  group_by(path, task) %>% 
  summarise(
    cor_a = cor(discrim_ml, discrim_word, method = "spearman"),
    cor_d = cor(diff_ml, diff_wrd, method = "spearman"),
    count = n()
  )
```

Correlations for each model and lexical class

```{r}
irt_params_joined %>% 
  group_by(path, lexical_class, task) %>% 
  summarise(
    cor_a = cor(discrim_ml, discrim_word, method = "spearman"),
    cor_d = cor(diff_ml, diff_wrd, method = "spearman"),
    count = n()
  )
```

Correlations for each model and category

```{r}
category_table <- 
  irt_params_joined %>% 
  group_by(path, category, task) %>% 
  summarise(
    cor_discrim = cor(discrim_ml, discrim_word, method = "spearman"),
    cor_diff = cor(diff_ml, diff_wrd, method = "spearman")
  ) %>% 
  ungroup() %>% 
  gather(-(path:task), key = "key", value = "value") %>% 
  mutate(value = round(value, digits = 3)) %>% 
  spread(category, value) %>% 
  mutate(
    data = if_else(path %in% c("babi_20_20_item_parameters.txt", "RUN_30_GPU_14_models_babi_all_words_item_parameters.txt"), "bAbI",
                   if_else(path %in% c("childes_20_20_item_parameters.txt", "RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt"), "Childes",
                           "Both")
                   )
  ) %>% 
  select(-sounds)
```


```{r}
clean_category_table <- 
  category_table %>% 
  mutate(
    task = if_else(task == "discrimination", "Understands", "Produces"),
    key = if_else(key == "cor_diff", "Difficulty", "Discrimination")
  ) %>%
  select(data, Task = task, Parameter = key, action_words:vehicles) %>% 
  rename(Dataset = data) %>% 
  arrange(Dataset, Task, Parameter)
  

cor_table <- 
  irt_params_joined %>% 
  group_by(path, task) %>% 
  summarise(
    cor_discrim = cor(discrim_ml, discrim_word, method = "spearman"),
    cor_diff = cor(diff_ml, diff_wrd, method = "spearman")
  ) %>% 
  ungroup() %>% 
  mutate(
    cor_discrim = round(cor_discrim, digits = 3),
    cor_diff = round(cor_diff, digits = 3)
  ) %>% 
  rename(Discrimination = cor_discrim, Difficulty = cor_diff, Task = task) %>% 
  mutate(
    data = if_else(path %in% c("babi_20_20_item_parameters.txt", "RUN_30_GPU_14_models_babi_all_words_item_parameters.txt"), "bAbI",
                   if_else(path %in% c("childes_20_20_item_parameters.txt", "RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt"), "Childes",
                           "Both")
                   ),
    Task = if_else(Task == "discrimination", "Understands", "Produces")
  ) %>% 
  rename(Dataset = data) %>% 
  select(Dataset, Task, Discrimination, Difficulty)
```

Make latex tables

```{r}
library("xtable")
xftbl <- xtable((as.data.frame(clean_category_table)))

xftbl2 <- xtable((as.data.frame(cor_table)))
```


```{r}
irt_params_joined %>% 
  group_by(path, task) %>% 
  summarise(
    cor_discrim = cor(discrim_ml, discrim_word, method = "spearman"),
    sig_discrim = cor.test(discrim_ml, discrim_word, method = "spearman")$p.value,
    cor_diff = cor(diff_ml, diff_wrd, method = "spearman"),
    sig_diff = cor.test(diff_ml, diff_wrd, method = "spearman")$p.value,
  ) %>% 
  ungroup() 
```


Summary stats 

```{r}
summary(irt_params_joined$discrim_ml)
summary(irt_params_joined$diff_ml)

summary(irt_params_joined$discrim_word)
summary(irt_params_joined$diff_wrd)
```


Histogram plots 

Babi
(Filtered out the few words with a value > 20)

```{r}
all_irt_item_outputs_babi <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("both_datasets_40_20_irt_models_item_parameters.txt",
             "RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt")
  ) %>% 
  gather(-definition, -path, -task, key = "key", value = "value") %>% 
  filter(value < 20) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  mutate(parameter = fct_recode(key, 
                                Discrimination = "discrim_ml", 
                                Difficulty = "diff_ml") %>%
           relevel("Difficulty"),
         measure = fct_relevel(task, "Understands"))

ggplot(all_irt_item_outputs_babi, 
       aes(x = value)) +
  geom_histogram(binwidth = .5) + 
  facet_grid(measure ~ parameter) + 
  # xlim(-5,5) + 
  xlab("Parameter value") + 
  ylab("Number of words") 
```

Childes
(Filtered out the few words with a value > 20)

```{r}
all_irt_item_outputs %>% count(path)

all_irt_item_outputs_childes <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("childes_20_20_item_parameters.txt",
             "RUN_29_GPU_14_models_Childes_all_words_item_parameters.txt")
  ) %>% 
  gather(-definition, -path, -task, key = "key", value = "value") %>% 
  filter(value < 20) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  mutate(parameter = fct_recode(key, 
                                Discrimination = "discrim_ml", 
                                Difficulty = "diff_ml") %>%
           relevel("Difficulty"),
         measure = fct_relevel(task, "Understands"))

ggplot(all_irt_item_outputs_childes, 
       aes(x = value)) +
  geom_histogram(binwidth = .5) + 
  facet_grid(measure ~ parameter) + 
  # xlim(-5,5) + 
  xlab("Parameter value") + 
  ylab("Number of words")
```

All data histograms

```{r}
all_irt_item_outputs_both <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt",
             "both_datasets_40_20_irt_models_item_parameters.txt")
  ) %>% 
  gather(-definition, -path, -task, key = "key", value = "value") %>% 
  filter(value < 20) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  mutate(parameter = fct_recode(key, 
                                Discrimination = "discrim_ml", 
                                Difficulty = "diff_ml") %>%
           relevel("Difficulty"),
         measure = fct_relevel(task, "Understands"))

ggplot(all_irt_item_outputs_both, 
       aes(x = value)) +
  geom_histogram(binwidth = .5) + 
  facet_grid(measure ~ parameter) + 
  # xlim(-5,5) + 
  xlab("Parameter value") + 
  ylab("Number of words")
```



Difficulty vs. Discrimination: Wordbank 

```{r}
a <- ggplot(coefs_2pl, 
       aes(x = a1, y = -d, col = lexical_class_label)) + 
  geom_point(alpha = .3) + 
  ggrepel::geom_text_repel(data = filter(coefs_2pl, 
                                a1 < 1 | a1 > 3.8 | -d > 5 | -d < -2.5), 
                  aes(label = definition), size = 2,
                  show.legend = FALSE) + 
  scale_colour_discrete(name = "Lexical class") + 
  xlab("Discrimination") + 
  ylab("Difficulty") +
  labs(title = "Worbank")

a
```

Childes, Produces

```{r}
all_irt_item_outputs_childes_lex <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("childes_20_20_item_parameters.txt",
             "RUN_29_GPU_14_models_Childes_all_words_item_parameters.txt")
  ) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  left_join(
    coefs_2pl %>% 
    select(definition, lexical_class),
    by = "definition"
  ) 
  
all_irt_item_outputs_childes_lex %>% 
  drop_na(lexical_class) %>% 
  filter(task == "Produces") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") 
```

Childes, Understands

```{r}
all_irt_item_outputs_childes_lex %>% 
  drop_na(lexical_class) %>% 
  #filter(discrim_ml < 20, task == "Understands") %>% 
  filter(task == "Understands") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") 
```


```{r}
all_irt_item_outputs_childes_lex %>% 
  drop_na(lexical_class) %>% 
  ggplot(aes(x = lexical_class, y = discrim_ml)) +
  geom_boxplot() +
  labs(x = "Lexical class", y = "Discrimination")

all_irt_item_outputs_childes_lex %>% 
  drop_na(lexical_class) %>% 
  ggplot(aes(x = lexical_class, y = diff_ml)) +
  geom_boxplot() +
  labs(x = "Lexical class", y = "Difficulty")
```


```{r}
all_irt_item_outputs_childes_lex %>% 
  left_join(
    coefs_2pl %>% 
    select(definition, category, lexical_class),
    by = "definition"
  ) %>% 
  ggplot(aes(x = category, y = discrim_ml)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=0))
```


Babi, Produces

```{r}
all_irt_item_outputs_babi_lex <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("babi_20_20_item_parameters.txt",
             "RUN_30_GPU_14_models_babi_all_words_item_parameters.txt")
  ) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  left_join(
    coefs_2pl %>% 
    select(definition, lexical_class),
    by = "definition"
  ) 
  
all_irt_item_outputs_babi_lex %>% 
  drop_na(lexical_class) %>% 
  filter(task == "Produces") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") 
```

```{r}
all_irt_item_outputs_babi_lex %>% 
  drop_na(lexical_class) %>% 
  filter(task == "Understands") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") 
```


```{r}
all_irt_item_outputs_babi_lex %>% 
  drop_na(lexical_class) %>% 
  ggplot(aes(x = lexical_class, y = discrim_ml)) +
  geom_boxplot() +
  labs(x = "Lexical class", y = "Discrimination")

all_irt_item_outputs_babi_lex %>% 
  drop_na(lexical_class) %>% 
  ggplot(aes(x = lexical_class, y = diff_ml)) +
  geom_boxplot() +
  labs(x = "Lexical class", y = "Difficulty")
```


All, Produces

```{r}
all_irt_item_outputs_all_lex <- 
  all_irt_item_outputs %>% 
  filter(
    path %in% c("both_datasets_40_20_irt_models_item_parameters.txt",
             "RUN_28_GPU_14_models_Childes_babi_all_words_item_parameters.txt")
  ) %>% 
  mutate(task = if_else(task == "generation", "Produces", "Understands")) %>% 
  left_join(
    coefs_2pl %>% 
    select(definition, lexical_class),
    by = "definition"
  ) 
  
all_irt_item_outputs_all_lex %>% 
  drop_na(lexical_class) %>% 
  filter(task == "Produces") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") +
  theme(legend.position = "bottom") 
```
All understands

```{r}
all_irt_item_outputs_all_lex %>% 
  drop_na(lexical_class) %>% 
  filter(task == "Understands") %>% 
  ggplot(aes(x = discrim_ml, y = -diff_ml, col = lexical_class)) +
  geom_point(alpha = .3) + 
  scale_colour_discrete(name = "Lexical class") + 
  scale_x_log10() +
  xlab("Discrimination") + 
  ylab("Difficulty") +
  theme(legend.position = "bottom") 
```



Summary stats 

```{r}
summary(irt_params_joined$discrim_ml)
summary(irt_params_joined$diff_ml)

summary(irt_params_joined$discrim_word)
summary(irt_params_joined$diff_wrd)
```


Barplots of the models

```{r}
mods_guy <- 
  c("babi_20_20_ability_parameters.txt","childes_20_20_ability_parameters.txt")

mods_ily <- c("RUN_30_GPU_14_models_babi_all_words_ability_parameters.txt","RUN_29_GPU_14_models_Childes_all_words_ability_parameters.txt")

mods_guy_paths <- str_c("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/", mods_ily)
mods_ily_paths <- str_c("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/discriminative/", mods_guy)
```


bAbI models

```{r}
babi_mods <- 
  read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/discriminative/babi_20_20_ability_parameters.txt") %>% 
  mutate(data = "bAbI", task = "Discrimination") %>% 
  rbind(
    read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/RUN_30_GPU_14_models_babi_all_words_ability_parameters.txt") %>% 
    mutate(data = "bAbI", task = "Generation")
  )

babi_mods %>% 
  filter(!name %in% c("all-1", "all-0")) %>% 
  mutate(task = if_else(task == "Generation", "Producing", "Understanding")) %>% 
  mutate(name = str_replace_all(name, "nyu-mll/", "")) %>% 
  mutate(category = if_else(
    str_detect(name, "roberta-base-1B"), "roberta-1B",
    if_else(str_detect(name, "roberta-base-10M"), "roberta-10M",
            if_else(str_detect(name, "roberta-base-100M"), "roberta-100M",
                    if_else(str_detect(name, "roberta-med-small-1M"), "roberta-1M",
                            name))))
  ) %>% 
  mutate(category = if_else(category == "bert-base-uncased", "bert",
                            if_else(category == "distilbert-base-uncased", "distilbert", category))) %>% 
  group_by(category, task) %>% 
  summarise(theta = mean(theta)) %>% 
  ungroup() %>% 
  ggplot(aes(category, theta, fill = task)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(fill = "Task", y = "Estimated latent ability", x = "Model") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=0), legend.position = "bottom") 
```

Childes models

```{r}
childes_mods <- 
  read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/discriminative/childes_20_20_ability_parameters.txt") %>% 
  mutate(data = "Childes", task = "Discrimination") %>% 
  rbind(
    read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/RUN_29_GPU_14_models_Childes_all_words_ability_parameters.txt") %>% 
    mutate(data = "Childes", task = "Generation")
  )


childes_mods %>% 
  filter(!name %in% c("all-1", "all-0")) %>% 
  mutate(task = if_else(task == "Generation", "Producing", "Understanding")) %>% 
  mutate(name = str_replace_all(name, "nyu-mll/", "")) %>% 
  mutate(category = if_else(
    str_detect(name, "roberta-base-1B"), "roberta-base-1B",
    if_else(str_detect(name, "roberta-base-10M"), "roberta-base-10M",
            if_else(str_detect(name, "roberta-base-100M"), "roberta-base-100M",
                    if_else(str_detect(name, "roberta-med-small-1M"), "roberta-base-1M",
                            name))))
  ) %>% 
  group_by(category, task) %>% 
  summarise(theta = mean(theta)) %>% 
  ungroup() %>% 
  ggplot(aes(category, theta, fill = task)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(fill = "Task", y = "Estimated latent ability", x = "Model") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=0)) 
```

```{r}
all_mods <- 
  read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/discriminative/both_datasets_40_20_irt_models_ability_parameters.txt") %>% 
  mutate(data = "Childes", task = "Discrimination") %>% 
  rbind(
    read_tsv("/Users/tymorcodes/GitHub_C/language-models-wordbank/output/RUN_28_GPU_14_models_Childes_babi_all_words_ability_parameters.txt") %>% 
    mutate(data = "Childes", task = "Generation")
  )


all_mods %>% 
  filter(!name %in% c("all-1", "all-0")) %>% 
  mutate(task = if_else(task == "Generation", "Producing", "Understanding")) %>% 
  mutate(name = str_replace_all(name, "nyu-mll/", "")) %>% 
  mutate(category = if_else(
    str_detect(name, "roberta-base-1B"), "roberta-1B",
    if_else(str_detect(name, "roberta-base-10M"), "roberta-10M",
            if_else(str_detect(name, "roberta-base-100M"), "roberta-100M",
                    if_else(str_detect(name, "roberta-med-small-1M"), "roberta-1M",
                            name))))
  ) %>% 
  mutate(category = if_else(category == "bert-base-uncased", "bert",
                            if_else(category == "distilbert-base-uncased", "distilbert", category))) %>% 
  group_by(category, task) %>% 
  summarise(theta = mean(theta)) %>% 
  ungroup() %>% 
  mutate(category = as.factor(category)) %>% 
  mutate(category = fct_relevel(category, "bert", "distilbert", "roberta-1B", "roberta-100M", "roberta-10M", "roberta-1M")) %>% 
  ggplot(aes(category, theta, fill = task)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(fill = "Task", y = "Estimated latent ability", x = "Model") +
  theme(axis.text.x = element_text(size = 10, angle = 0), legend.position = "bottom") 
```



